Embodied Neuromorphic Benchmarks

### 2015-08-10 paper/paper.tex
online
min sim for adapt control

    Evaluating the effectiveness and performance of neuromorphic hardware is
    difficult.  It is even more difficult when the task of interest is an
    embodied task; that is, a task where the output from the neuromorphic
    hardware affects its future input.  However, these embodied situations
    are one of the primary potential uses of neuromorphic hardware.  To address
    this, we present a methodology for embodied benchmarking and a particular
    example of a benchmark for adaptive control of an arbitrary system.  These
    benchmarks are flexible, in that they allow researchers to explicitly
    modify the benchmark to identify particular task domains where particular
    hardware excels.  Furthermore, the benchmarks make use of a hybrid of
    real physical embodiment and a type of "minimal" simulation that has been
    shown to lead to robust real-world performance, allowing the same benchmark
    to be used by many researchers.

@@

However, \emph{not} using a real physical embodiment for testing is also
problematic.  First and foremost, without an actual real-world task, why
should anyone have any confidence that the performance on the benchmark is
reflective of the actual usefulness of the neuromorphic hardware?  It is
very widely known that \emph{simulations of robots} (or other physical systems) are
often much easier to control and better-behaved than the real thing.  The
field of robotics is filled with algorithms that work well ``in theory'', but
fail when run on actual hardware.  We do not want a benchmark that falls into
this trap of failing to generalize to real situations.

@@

The above considerations seem to indicate that even though using real-world
phyiscal hardware for benchmarking is problematic, it is still better than
using simplistic simulations which may not generalize to real tasks.  However,
we believe there is an alternate approach known as \emph{Minimal Simulation}
\cite{Jakobi97evolutionaryrobotics}.

@@

The simplest controller for such a situation is a P (proportional) controller,
where $u=K_p(q_d - q)$.  This is often supplemented with a derivative term,
which helps to slow the system down as it approaches the desired position,
thus avoiding overshooting and oscillation ($u=K_p(q_d - q) + K_d(\dot{q_d} - \dot{q})$),
leading to the standard PD controller.  Both $K_p$ and $K_d$ are constants that can be
hand-tuned to particular situations.

However, this controller has difficulty in the presence of significant external
forces.  For example, consider a single motor controlling the angle of a single
arm.  If the arm is held out to the side, gravity acting on the mass of the
arm itself will pull the arm downward.  Thus to hold the arm still at a
particular $q_d$ will require the controller to apply a force to counteract
gravity.  Since the PD controller always produces an output $u=0$ when $q=q_d$,
it cannot compensate for this. [TODO: add diagram]

@@

In some robotics applications, the solution to this problem is to mathematically
analyze the geometry and mass of the system and compute exactly how much extra
force is needed.  In this particular case, the answer is straight-forward,
in that the extra torque due to gravity is $\tau=m l g sin(q) / 2$, where
$m$ is the mass of the arm, $l$ is the length, and $g$ is $9.8m/s^2$.  If the
force applied by the motor is linear in $u$, then we could simply compute this
value and add it to our controller's output.  However, this assumes a perfectly
even distribution of weight in the arm, ignores momentum and other forces, and 
gets much more complex as more joints are added.  Furthermore, if this
initial computation is slightly off, or if details of the system change,
there is no way to adjust this compensation.

Fortunately, there is an adaptive solution to this problem, and it is one that
fits well with neuromorphic hardware.  In \cite{Slotine1987}, Slotine shows that if you
express the influence of these other external forces as $\tau=Y(q) \omega$
(where $Y(q)$ is a fixed set of functions of $q$, such as $sin(q)$, and \omega
is a vector of weights, one for each function in $Y$), then you can learn
to compensate for these external forces by using the learning rule $\Delta \omega = \alpha Y(q) u$,
where $u$ is the basic PD control signal.

@@

\subsection{Online versus offline learning}

The one major step here that does not exist in a lot of neuromorphic hardware is
the ability to update the weights $d$.  For hardware that does have a built-in
learning rule, this rule is at least of a very common form, where the weight
update from a neuron is proportional to the activity of that neuron and an
external error signal.  This makes it an instance of the ubiquitous delta rule.

@@

% For Original Research Articles, Clinical Trial Articles, and Technology Reports the introduction should be succinct, with no subheadings.
%
% For Clinical Case Studies the Introduction should include symptoms at presentation, physical exams and lab results.
%
Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text. Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text. Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text.Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text.

%\begin{methods}
\section{Material \& Methods}

Text Text Text Text Text Text  Text Text Text Text Text Text \cite{conference} Text Text Text  Text Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text  Text Text.  \cite{patent} might want to know about  text text text text Text Text Text Text  Text Text Text Text Text Text  Text Text. \citep{article} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text  Text Text.  \cite{book} might want to know about  text text text text \cite{chapter}

\begin{table}[!t]
\textbf{\refstepcounter{table}\label{Tab:01} Table \arabic{table}.}{ Maximum size of the Manuscript }

\processtable{ }
{\begin{tabular}{lllll}\toprule
 & Abstract max. legth (incl. spaces) & Figures or tables & Manuscript max. length \\\midrule
Clinical Case Study & & & &\\
Clinical Trial & & & &\\
Hypothesis and Theory & & & &\\
Methods & 2000 characters  & 15 & 12000 words \\
Original Research & & & &\\
Review & & & &\\
Technology Report & & & &\\\midrule
Focused Review & 2000 characters & 5 & 5000 words \\\midrule
CPC &  1250 characters& 6 & 2500 words  \\\midrule
Perspective & 1250 characters & 2 & 3000 words  \\
Mini Review & & & &\\\midrule
Data Report & None & 2 & 3000 words\\\midrule
Classification & 1250 characters & 10 & 2000 words \\\midrule
Editorial & None & None & 1000 words  \\\midrule
Frontiers Commentary  & & &\\
General Commentary & None & 1 & 1000 words\\
Book review & & & \\\midrule
Opinion   & & &\\
Specialty Grand Challenge & None & 1 & 2000 words\\
Field Grand Challenge & & & &\\\botrule
\end{tabular}}{}
\end{table}

Please note that large tables covering several pages cannot be included in the final PDF for formatting reasons. These tables will be published as supplementary material on the online article abstract page at the time of acceptance. The author will notified during the typesetting of the final article if this is the case. A link in the final PDF will direct to the online material.

\subsection{Original Research Articles, Clinical Trial Articles, and Technology Reports}

For Original Research Articles, Clinical Trial Articles, and Technology Reports the section headings should be those appropriate for your field and the research itself. It is recommended to organize your manuscript in the following sections or their equivalents for your field:

\begin{itemize}
%for bulleted list, use itemize
\item Introduction: Succinct, with no subheadings.
\item Materials and Methods: This section may be divided by subheadings. This section should contain sufficient detail so that when read in conjunction with cited references, all procedures can be repeated.
\item Results: This section may be divided by subheadings. Footnotes should not be used and have to be transferred into the main text.
\item Discussion: This section may be divided by subheadings. Discussions should cover the key findings of the study: discuss any prior art related to the subject so to place the novelty of the discovery in the appropriate context; discuss the potential short-comings and limitations on their interpretations; discuss their integration into the current understanding of the problem and how this advances the current views; speculate on the future direction of the research and freely postulate theories that could be tested in the future.
\end{itemize}

Please note that the Material and Methods section can be placed in any of the following ways: before Results, before Discussion or after Discussion.

\subsection{Clinical Case Studies}

For Clinical Case Studies the following sections are mandatory:

\begin{itemize}
%for bulleted list, use itemize
\item Introduction: Include symptoms at presentation, physical exams and lab results.
\item Background: This section may be divided by subheadings. Include history and review of similar cases.
\item Results: This section may be divided by subheadings. Include diagnosis and treatment.
\item Concluding Remarks
\end{itemize}

%\end{methods}

\section{Results}

\subsection{Figures}
Frontiers requires figures to be submitted individually, in the same order as they are referred to in the manuscript. Figures will then be automatically embedded at the bottom of the submitted manuscript. Kindly ensure that each table and figure is mentioned in the text and in numerical order. Permission must be obtained for use of copyrighted material from other sources (including the web). Please note that it is compulsory to follow figure instructions. Figures which are not according to the guidelines will cause substantial delay during the production process.

\begin{table}[!t]
\textbf{\refstepcounter{table}\label{Tab:02} Table \arabic{table}.}{ Resolution Requirements for the figures}

\processtable{}
{\begin{tabular}{lllll}\toprule
Image Type & Description & Format & Color Mode & Resolution\\\midrule
Line Art & An image composed of lines and text,  & TIFF, JPEG & RGB, Bitmap & 900 - 1200 dpi\\
           & which does not contain tonal or shaded areas.& & &\\
           Halftone & A continuous tone photograph, which contains no text. & TIFF, EPS, JPEG & RGB, Grayscale & 300 dpi\\
Combination & Image contains halftone + text or line art elements. & TIFF, JPEG & RGB,Grayscale & 600 - 900 dpi\\\botrule
\end{tabular}}{}
\end{table}

\textbf{Table \ref{Tab:02}} shows the resolution requirements for the figures. The figures must be legible:
\begin{enumerate}
\item The smallest visible text is no less than 8 points in height, when viewed at actual size.
\item Solid lines are not broken up.
\item Image areas are not pixelated or stair stepped.
\item Text is legible and of high quality.
\item Any lines in the graphic are no smaller than 2 points width.
\item The actual size of the figure must be of at least 8.5 cm.
\end{enumerate}

\subsection{Nomenclature}
\begin{itemize}
\item The use of abbreviations should be kept to a minimum. Non-standard abbreviations should be avoided unless they appear at least four times, and defined upon first use in the main text. Consider also giving a list of non-standard abbreviations at the end, immediately before the Acknowledgments.
\item Gene symbols should be italicized; protein products are not italicized.
\item Chemical compounds and biomolecules should be referred to using systematic nomenclature, preferably using the recommendations by IUPAC.
\item We encourage the use of Standard International Units in all manuscripts.
\item To take part in the Resource Identification Initiative, please cite antibodies, genetically modified organisms, software tools, data, databases and services using the corresponding catalog number and RRID in your current manuscript. For more information about the project and for steps on how to search for an RRID, please click \href{http://www.frontiersin.org/files/pdf/letter_to_author.pdf}{here}.
\end{itemize}

\begin{equation}
\sum x+ y =Z\label{eq:01}
\end{equation}

\section{Discussion}

Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text Text.
Additional Requirements:
\subsection{Corrections}

If you need to communicate important changes to a published article please submit a General Commentary. Submit the article with the title “Corrigendum: Original Title of Article”.

\subsection{Commentaries on Articles}

At the beginning of your Commentary, please provide the citation of the article commented on. Rebuttals may be submitted in response to Commentaries; our limit in place is one commentary and one response. Rebuttals should also be submitted as General Commentary articles.

\subsection{Human Search and Animal Research}

All experiments on live vertebrates or higher invertebrates must be performed in accordance with relevant institutional and national guidelines and regulations. In the manuscript, authors must identify the committee approving the experiments and must confirm that all experiments conform to the relevant regulatory standards. For manuscripts reporting experiments on human subjects, authors must identify the committee approving the experiments and must also include a statement confirming that informed consent was obtained from all subjects. In Original Research Articles and Clinical Trial Articles these statements should appear in the Materials and Methods section.

\subsection{Clinical Trial Registration}

Clinical trials should be registered in a public trials registry in order to become the object of a publication at Frontiers. Trials must be registered at or before the start of patient enrollment. A clinical trial is defined as "any research study that prospectively assigns human participants or groups of humans to one or more health-related interventions to evaluate the effects on health outcomes."(\href{www.who.int/ictrp/en}{www.who.int/ictrp/en}). A list of acceptable registries can be found at \href{www.who.int/ictrp/en}{www.who.int/ictrp/en} and \href{www.icmje.org}{www.icmje.org}.

\subsection{Inclusion of Proteomics Data}

Authors should provide relevant information relating to how the peptide/protein matches were undertaken, including methods used to process and analyze data, false discovery rates (FDR) for large-scale studies and threshold or cut-off rates for peptide and protein matches. Further information could include software used, mass spectrometer type, sequence database and version, number of sequences in database, processing methods, mass tolerances used for matching, variable/fixed modifications, allowable missed cleavages, etc.

Authors should provide as supplementary material information used to identify proteins and/or peptides. This should include information such as accession numbers, observed mass (m/z), charge, delta mass, matched mass, peptide/protein scores, peptide modification, miscleavages, peptide sequence, match rank, matched species (for cross species matching), number of peptide matches, ambiguous protein/peptide matches should be indicated, etc.
For quantitative proteomics analyses authors should provide information to justify the statistical significance including biological replicates, statistical methods, estimates of uncertainty and the methods used for calculating error.

For peptide matches with biologically relevant post-translational modifications (PTM) and for any protein match that has occurred using a single mass spectrum, authors should include this information as raw data, annotated spectra or submit data to an online repository (recommended option).
Authors are encouraged to submit raw or matched data and 2-DE images to public proteomics repositories. Submission codes and/or links to data should be provided within the manuscript.

\subsection{Data Sharing}

Frontiers supports the policy of data sharing, and authors are advised to make freely available any materials and information described in their article, and any data relevant to the article (while not compromising confidentiality in the context of human-subject research) that may be reasonably requested by others for the purpose of academic and non-commercial research. In regards to deposition of data and data sharing through databases, Frontiers urges authors to comply with the current best practices within their discipline.

@@

\section*{Author Contributions}
%When determining authorship the following criteria should be observed:
%•	Substantial contributions to the conception or design of the work; or the acquisition, analysis, or interpretation of data for the work; AND
%•	Drafting the work or revising it critically for important intellectual content; AND
%•	Final approval of the version to be published ; AND
%•	Agreement to be accountable for all aspects of the work in ensuring that questions related to the accuracy or integrity of any part of the work are appropriately investigated and resolved.
%Contributors who meet fewer than all 4 of the above criteria for authorship should not be listed as authors, but they should be acknowledged. (http://www.icmje.org/roles_a.html)

The statement about the authors and contributors can be up to several sentences long, describing the tasks of individual authors referred to by their initials and should be included at the end of the manuscript before the References section.

@@

\section*{Supplemental Data}
Supplementary Material should be uploaded separately on submission, if there are Supplementary Figures, please include the caption in the same file as the figure. LaTeX Supplementary Material templates can be found in the Frontiers LaTeX folder

Text Text Text Text Text Text  Text Text Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text.

>>>>

    Evaluating the effectiveness and performance of neuromorphic hardware is
    difficult.  It is even more difficult when the task of interest is an
    embodied task; that is, a task where the output from the neuromorphic
    hardware affects its future input.  However, these embodied situations
    are one of the primary potential uses of neuromorphic hardware.  To address
    this, we present a methodology for embodied benchmarking and a particular
    example of a benchmark for adaptive control of an arbitrary system.  These
    benchmarks are flexible, in that they allow researchers to explicitly
    modify the benchmark to identify particular task domains where particular
    hardware excels.  Furthermore, the benchmarks make use of a hybrid of
    real physical embodiment and a type of ``minimal'' simulation that has been
    shown to lead to robust real-world performance, allowing the same benchmark
    to be used by many researchers.

@@

However, \emph{not} using a real physical embodiment for testing is also
problematic.  First and foremost, without an actual real-world task, why
should anyone have any confidence that the performance on the benchmark is
reflective of the actual usefulness of the neuromorphic hardware?  It is
very widely known that \emph{simulations of robots} (or other physical systems) are
often much easier to control and better-behaved than the real thing.  The
field of robotics is filled with algorithms that work well ``in theory,'' but
fail when run on actual hardware.  We do not want a benchmark that falls into
this trap of failing to generalize to real situations.

@@

The above considerations seem to indicate that even though using real-world
phyiscal hardware for benchmarking is problematic, it is still better than
using simplistic simulations which may not generalize to real tasks.  However,
we believe there is an alternate approach known as \emph{Minimal Simulation}
(\citealt{Jakobi97evolutionaryrobotics}).

@@

The simplest controller for such a situation is a P (proportional) controller,
where $u=K_p(q_d - q)$.  This is often supplemented with a derivative term,
which helps to slow the system down as it approaches the desired position,
thus avoiding overshooting and oscillation ($u=K_p(q_d - q) + K_d(\dot{q_d} - \dot{q})$),
leading to the standard PD controller.  Both $K_p$ and $K_d$ are constants that can be
tuned to particular situations.

However, this controller has difficulty in the presence of significant external
forces.  For example, consider a single motor controlling the angle of a single
arm.  If the arm is held out to the side, gravity acting on the mass of the
arm itself will pull the arm downward.  Thus to hold the arm still at a
particular $q_d$ will require the controller to apply a force to counteract
gravity.  Since the PD controller always produces an output $u=0$ when $q=q_d$,
it cannot compensate for this, and so the arm will stay stationary at some
angle below the desired angle. [TODO: add diagram]

@@

In some robotics applications, the solution to this problem is to mathematically
analyze the geometry and mass of the system and compute exactly how much extra
force is needed.  In this particular case, the answer is straight-forward,
in that the extra torque due to gravity is $\tau=mg {l \over 2} sin(q)$, where
$m$ is the mass of the arm, $l$ is the length, and $g$ is $9.8m/s^2$.  If the
force applied by the motor is linear in $u$, then we could simply compute this
value and add it to our controller's output.  However, this assumes a perfectly
even distribution of weight in the arm, ignores momentum and other forces, and 
gets much more complex as more joints are added.  Furthermore, if this
initial computation is slightly off, or if details of the system change,
there is no way to adjust this compensation.

Fortunately, there is an adaptive solution to this problem, and it is one that
fits well with neuromorphic hardware.  \cite{Slotine1987} shows that if you
express the influence of these other external forces as $\tau=Y(q) \omega$
(where $Y(q)$ is a fixed set of functions of $q$, such as $sin(q)$, and $\omega$
is a vector of weights, one for each function in $Y$), then you can learn
to compensate for these external forces by using the learning rule $\Delta \omega = \alpha Y(q) u$,
where $u$ is the basic PD control signal.

@@

\subsection{Online and offline learning}

The one major step here that does not exist in a lot of neuromorphic hardware is
the ability to update the weights $d$.  For hardware that does have a built-in
learning rule, this rule is at least of a very common form, where the weight
update from a neuron is proportional to the activity of that neuron and an
external error signal.  This makes it an instance of the ubiquitous delta rule,
and hopefully supported by the hardware.

@@

\subsection{Minimal Simulation for Adaptive Control}

Now that we have defined the task, we can use the principles of Minimal
Simulation to construct a flexible and variable simulated environment for
testing adaptive control.  The idea is to make a bare-bones simulation of
the system being controlled, with built-in variability.  If the neuromorphic
controller works well across this variability, then it is likely to work well
outside of simulation as well.

The basic system variable is a vector of length $N$ holding the joint angles $q$.  
Each joint has a velocity $v$.  The force applied by each motor is 
related to the signal sent to the motor $u$, but will generally have some
maximum value $T$, so we use $tanh(u)T$. For friction, we 
simply scale the velocity by some factor $F$ every time step.  
This results in the simplistic simulation as follows:

\begin{align}
    \Delta v & =  -v F + tanh(u)T \\
    \Delta q & = v
\end{align}

On top of this, we need to add the external force for which the adaptive system
is trying to compensate.  Rather than deciding on what specific external
force, we \emph{randomly generate} an equation controlling this force.  We start with a small set of
smooth functions on $X$ which are often found in dynamics equations ($x$, $x^2$,
$sin(x)$).  We then generate an external force of $Q (\zeta X(\beta q + \gamma) + \eta)$
where $\zeta$, $\beta$, $\gamma$, and $\eta$ are all randomly chosen fron $N(0,1)$
and $Q$ is a scaling factor to control how strong this external force is.  The
result is added to Equation 1.

Finally, we add random noise, delay, and filtering to both the input and the
output of the system.  For noise, we add $N(0,\sigma_u)$ to the control signal
$u$ and $N(0,\sigma_q)$ to the $q$ value reported back to the controller.  We
also use a low-pass filter to smooth both values (with time constants $\tau_u$
and $\tau_q$) after this noise is added.  Finally, both $q$ and $u$ are delayed
by an amount of time $t_q$ and $t_u$.

The result is not meant to be a simulation of a particular physical embodiment.
Rather, the variability in this simulation is meant to be extremely fast
to simulation, and to make it hard to ``cheat''
to control it.  In other words, if a controller manages to be able to control
the various randomly created minimal simulations of embodiment that are
generated with this approach, then we have reason to believe that it will also
be successful at controlling real embodiments.  With this simulation and
modern computers, we can easily simulate in real-time systems with dozens of joints and
highly complex interactions between them, and measure how well an adaptive
controller deals with these situations.

\subsection{Cheap Robotics for Adaptive Control}

@@

@@
